
---
title: "INA Plots"
author: "Bartol Freškura"
date: "September 26, 2015"
output:
      html_document:
            highlight: tango
            toc: yes
---

```{r echo=FALSE}
##SCRIPT FOR CONVERTING DATA FROM SURVEY CSV TO R DATA STRUCTURES

#' @name Convert from csv to data frame
#' @author Bartol Freškura
#' @description Converts raw csv file from survey to a R data structure in a form of data frame
#' @param path Path to folder where .csv files is locatde
#' @param fileName Name of the .csv file
#' @return Data frame with processed data
#' @example convertToRData("/home/username/Documents/Project/CSVDir/", "sample_survey.csv")
convertToRData <- function(path, fileName){
      
      ##CONSTANTS
      #LOCAL path for csv files
      pathCsv <- path
      
      
      #Types of attributes in columns
      columnTypes <- c("character","character","character","integer","integer","integer","integer",
                       "integer", "character", "character", "character", "character", "character", "character"
                       , "character", "character", "character", "character","character","character")
      
      #Column names
      columnNames <- c("ID.Hash","Sex","Age","Student.Status","Employer.Opinion","National.Identity",
                       "Employee.Satisfaction","Future.Employee","Work.Field","Industry","Creativity","Ecology",
                       "Science","Energetics","Croatia","Association.Career", "E.Mail", "Start.Date","End.Date",
                       "Network.ID")
      
      ##Load data
      rawData <- read.csv(paste(pathCsv,fileName, sep = ''),header = TRUE, na.strings = "",
                          colClasses = columnTypes, comment.char = "")
      #Set column names
      colnames(rawData) <- columnNames
      
      
      ##### QUESTION CONSTANTS ############
      
      ##Koja je vaša dobna skupina?*
      #constants
      to17 <- "do 17"
      from18To20 <- "od 18 do 20"
      from21To23 <- "od 21 do 23"
      from23To26 <- "od 24 do 26"
      from27Above <- "27 ili stariji"
      
      
      #Koje područje poslovanja INA grupacije smatrate osobno najzanimljivijim?*
      #constants
      research <- "Istraživanje i proizvodnja nafte i plina"
      rafinery <- "Rafinerije i marketing"
      finance <- "Financije"
      it_sup <- "IT potpora"
      logistics <- "Logistička potpora"
      
      ##### QUESTION CONSTANTS ############
      
      
      #Create vectors for modified data frame
      id <- character()
      sex <- character()
      age <- character()
      student.status <- integer()
      employer.opinion <- integer()
      national.identity <- integer()
      employee.satisfaction <- integer()
      future.employee <- integer()
      work.field <- character()
      ina.association <- character()
      association.career <- character()
      email <- character()
      start.date <- date()
      end.date <- date()
      network.id <- character()
      
      #Iterate through data frame and do the conversion
      
      for (i in 1:nrow(rawData)) {
            #Handle ID hash
            id <- c(id, rawData[i,]$ID.Hash)
            
            #Handle sex (hueuheuhueuhe69)
            if(rawData[i,2]=="muško"){
                  sex <- c(sex,"M")
            }
            else{
                  sex <- c(sex,"F")
            }
            
            #Handle Age
            if(rawData[i,3]==to17){
                  age <- c(age, "0-17")
            }
            else if(rawData[i,3]==from18To20){
                  age <- c(age, "18-20")
            }
            else if(rawData[i,3]==from21To23){
                  age <- c(age, "21-23")
            }
            else if(rawData[i,3]==from23To26){
                  age <- c(age, "24-26")
            }
            else{
                  age <- c(age, "27-Inf")
            }
            
            #Handle student status
            # 1== STUDENT_TRUE, 0== STUDENT_FALSE
            student.status <- c(student.status, rawData[i,]$Student.Status)
            
            #Handle Employer opinion
            employer.opinion <- c(employer.opinion, rawData[i,]$Employer.Opinion)
            
            #Handle National Identity rating
            national.identity <- c( national.identity , rawData[i,]$National.Identity)
            
            #Handle Employee satifaction
            employee.satisfaction <- c(employee.satisfaction, rawData[i,]$Employee.Satisfaction)
            
            #Handle future employee
            future.employee <- c(future.employee, rawData[i,]$Future.Employee)
            
            #Handle Work field
            if(rawData[i,]$Work.Field==it_sup){
                  work.field <- c(work.field, "IT_Support")
            }
            
            else if(rawData[i,]$Work.Field==research){
                  work.field <- c(work.field, "Research_Production_Oil_Gas")
            }
            
            else if(rawData[i,]$Work.Field==finance){
                  work.field <- c(work.field, "Finances")
            }
            
            else if(rawData[i,]$Work.Field==rafinery){
                  work.field <- c(work.field, "Rafinery_Marketing")
            }
            
            else{
                  work.field <- c(work.field, "Logistics")
            }
            
            
            #Handle INA association
            
            #define temp variables
            ind <- toString(rawData[i,]$Industry)
            cre <- toString(rawData[i,]$Creativity)
            eco <- toString(rawData[i,]$Ecology)
            sci <- toString(rawData[i,]$Science)
            en <- toString(rawData[i,]$Energetics)
            cro <- toString(rawData[i,]$Croatia)
            ##MAGIC :D
            newVec <- paste(ind,cre,eco,sci,en,cro, sep = ";")
            newVec <- gsub(pattern = ";NA", x = newVec, replacement = "")
            newVec <- gsub(pattern = ";;", x = newVec, replacement = "")
            newVec <- gsub(pattern = "NA;", x = newVec, replacement = "")
            ina.association <- c(ina.association, newVec)
            
            
            #Handle Association career
            association.career <- c(association.career, rawData[i,]$Association.Career)
            
            #Handle E-mail
            email <- c(email, rawData[i,]$E.Mail)
            
            #Handle Network ID
            network.id <- c(network.id, rawData[i,]$Network.ID)
            
      }
      
      #Store to new data frame
      dataProc <- data.frame(id,sex,age,student.status,employer.opinion,national.identity,employee.satisfaction,
                             future.employee,work.field,ina.association,association.career,email,network.id)
      
      dataProc
}


```


##Load data
```{r}
library(ggplot2)
path <- "/mnt/8C1A960B1A95F286/Bartol_work/INA_Career_LOGO/resources/"
name <- "sample_survey.csv"
data <- convertToRData(path,name)
```

##Plotting Sex

```{r fig.width = 10, fig.height = 7}
plot <- ggplot(data = data, aes(x=sex, fill=sex)) + coord_cartesian(ylim=c(0,nrow(data)))
plot <- plot + geom_bar(width=0.5) + xlab("Sex") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + scale_fill_discrete(name="Sex", breaks=c("F", "M"), labels=c("Female", "Male"))
plot <- plot + scale_x_discrete(breaks=NULL)
plot <- plot + ggtitle("Your sex?")
plot
```

###Sex Analysis
```{r}
prop.table(table(data$sex))*100

```
Female percentage: XX.XX  
Male percentage: XX.XX



##Plotting Age

```{r fig.width = 10, fig.height = 7}
plot <- ggplot(data = data, aes(x=age, fill=age)) + coord_cartesian(ylim=c(0,nrow(data)))
plot <- plot + geom_bar(width=0.5) + xlab("Age") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + scale_fill_discrete(name="Age", breaks=c("0-17", "18-20","21-23","24-26","27-Inf"), 
                                   labels=c ("17 and below", "18 to 20", "21 to 23", "24 to 26", "27 or more"))
plot <- plot + scale_x_discrete(breaks=NULL)
plot <- plot + ggtitle("Your age?")
plot
```
###Age Analysis
```{r}
prop.table(table(data$age))*100

```
Below 17 percentage: XX.XX  
18-20 percentage: XX.XX  
21-23 percentage: XX.XX  
24-26 percentage: XX.XX  
27 and above percentage: XX.XX



##Plotting Student status

```{r fig.width = 10, fig.height = 7}
plot <- ggplot(data = data, aes(x=as.factor(student.status), fill=as.factor(student.status))) + coord_cartesian(ylim=c(0,nrow(data)))
plot <- plot + geom_bar(width=0.5) + xlab("Student status") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + scale_fill_discrete(name="Sex", breaks=c(1, 0), labels=c("Student", "Not Student"))
plot <- plot + scale_x_discrete(breaks=NULL)
plot <- plot + ggtitle("Are you a student?")
plot
```

###Student status Analysis
```{r}
## 0==NOT student, 1==Student
prop.table(table(data$student.status))*100

```
Not student percentage: XX.XX  
Student percentage: XX.XX



##Plotting Employer opinion

```{r fig.width = 10, fig.height = 7}
plot <- ggplot(data = data, aes(x=as.factor(employer.opinion))) + coord_cartesian(ylim=c(0,nrow(data)*0.6))
plot <- plot + geom_bar(width=0.5, fill="deepskyblue3") + xlab("Employer rating") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + ggtitle("Your opinion on INA as an employer")
plot
```

###Employer opinion Analysis
```{r}
#Percentages by rating given
prop.table(table(data$employer.opinion))*100

mean <- mean(data$employer.opinion)

summary(data$employer.opinion)
sd <- sd(data$employer.opinion)

#Calculating 95% confidence interval
error <- qnorm(0.975)*sd/sqrt(nrow(data))
left <- mean - error
right <- mean + error

cat(paste("95% confidence interval:", left, "-", right, sep = " "))

```
Mean rating: XX.XX  
Standard deviation: XX.XX  
95% confidence interval: XX.XX - XX-XX  


##Plotting National identity

```{r fig.width = 10, fig.height = 7}
plot <- ggplot(data = data, aes(x=as.factor(national.identity))) + coord_cartesian(ylim=c(0,nrow(data)*0.40))
plot <- plot + geom_bar(width=0.5, fill="deepskyblue3") + xlab("National Identity rating") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + ggtitle("How much do you associate INA with Croatia and the croatian national identity?" )
plot
```

###National identity Analysis
```{r}
#Percentages by rating given
prop.table(table(data$national.identity))*100

mean <- mean(data$national.identity)

summary(data$national.identity)
sd <- sd(data$national.identity)

#Calculating 95% confidence interval
error <- qnorm(0.975)*sd/sqrt(nrow(data))
left <- mean - error
right <- mean + error

cat(paste("95% confidence interval:", left, "-", right, sep = " "))

```
Mean rating: XX.XX  
Standard deviation: XX.XX  
95% confidence interval: XX.XX - XX-XX  



##Plotting Employee satisfaction

```{r fig.width = 10, fig.height = 7}
plot <- ggplot(data = data, aes(x=as.factor(employee.satisfaction), fill=as.factor(employee.satisfaction))) + coord_cartesian(ylim=c(0,nrow(data)))
plot <- plot + geom_bar(width=0.5) + xlab("Yes or no") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + scale_fill_discrete(name="", breaks=c(1, 0), labels=c("Yes", "No"))
plot <- plot + scale_x_discrete(breaks=NULL)
plot <- plot + ggtitle("Would you consider yourself satisfied as an employee in one of the fields of work that INA offers?")
plot
```

###Employee satisfaction Analysis
```{r}
## 0==Wouldn't be satisfied , 1==Would be satisfied
prop.table(table(data$employee.satisfaction))*100

```
Yes: XX.XX  
No: XX.XX




##Plotting Future employee

```{r fig.width = 10, fig.height = 7}
plot <- ggplot(data = data, aes(x=as.factor(future.employee), fill=as.factor(future.employee))) + coord_cartesian(ylim=c(0,nrow(data)))
plot <- plot + geom_bar(width=0.5) + xlab("Yes or no") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + scale_fill_discrete(name="", breaks=c(1, 0), labels=c("Yes", "No"))
plot <- plot + scale_x_discrete(breaks=NULL)
plot <- plot + ggtitle("Do you see yourself as a potential employee of the INA company?")
plot
```

###Future employee Analysis
```{r}
## 0==Doesn't see as employee , 1==See as employee
prop.table(table(data$future.employee))*100

```
Yes: XX.XX  
No: XX.XX  
Ovdje možes naglasiti da iaoko puno ljudi bi bilo zadovoljno radom u INA-i, ne bih ih toliko htjelo
raditi tamo



##Plotting Work field

```{r fig.width = 10, fig.height = 7}

plot <- ggplot(data = data, aes(x=work.field, fill=work.field)) + coord_cartesian(ylim=c(0,nrow(data)*0.45))
plot <- plot + geom_bar(width=0.5) + xlab("Field of work") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + scale_fill_discrete(name="Field of work", breaks=c("Finances","IT_Support", "Logistics","Rafinery_Marketing","Research_Production_Oil_Gas"), 
                                   labels=c("Finances", "IT Support", "Logistics", "Rafinery or Marketing",
                                            "Research and production of\n Oil and Gas"))
plot <- plot + scale_x_discrete(breaks=NULL)
plot <- plot + ggtitle("Which field of work that INA offers do you consider the most interesting?")
plot
```

###Work field Analysis
```{r}
prop.table(table(data$work.field))*100

```
Finances: XX.XX  
IT Support: XX.XX  
Logistics: XX.XX  
Rafinery or Marketing: XX.XX  
Research and production of Oil and Gas: XX.XX






##Plotting INA Association

```{r echo=FALSE}
#Etracting levels into seperate categories
industry <- character()
creativity <- character()
ecology <- character()
science <- character()
energetics <- character()
croatia <- character()

for(i in 1:nrow(data)){
      #split values into list
      tempList <- strsplit(x=as.character(data[i,]$ina.association), split = ';')
      
      #convert to vector
      tempVec <- unlist(tempList)
      for(j in 1:length(tempVec)){
            if(tempVec[j]=="Kreativnost"){
                  creativity <- c(creativity,tempVec[j])
            }
            else if(tempVec[j]=="Industrija"){
                  industry <- c(industry,tempVec[j])
            }
            else if(tempVec[j]=="Energetika"){
                  energetics <- c(energetics,tempVec[j])
            }
            else if(tempVec[j]=="Ekologija"){
                  ecology <- c(ecology,tempVec[j])
            }
            else if(tempVec[j]=="Znanost"){
                  science <- c(science,tempVec[j])
            }
            else{
                  croatia <- c(croatia,tempVec[j])
            }
      }
      
}


#create new data frame
unifiedVector <- c(industry,croatia,creativity,ecology,science,energetics)
frameINAAssociation <- data.frame(unifiedVector)
colnames(frameINAAssociation) <- c("ina.association")
```



```{r fig.width = 10, fig.height = 7}
#PLOTTING
plot <- ggplot(data = frameINAAssociation, aes(x=ina.association, fill=ina.association)) + coord_cartesian(ylim=c(0,nrow(frameINAAssociation)*0.5))
plot <- plot + geom_bar(width=0.5) + xlab("INA Association") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=17), axis.title=element_text(size=17))
plot <- plot + scale_fill_discrete(name="Associations", breaks=c("Ekologija","Energetika", "Hrvatska","Industrija","Kreativnost","Znanost"), 
                                   labels=c("Ecology", "Energetics", "Croatia", "Industry",
                                            "Creativity","Science"))
plot <- plot + scale_x_discrete(breaks=NULL)
plot <- plot + ggtitle("Which of following words would best describe your vision on INA as a company" )

plot
```

###INA Association Analysis
```{r}
prop.table(table(frameINAAssociation$ina.association))*100

```
Ekologija: XX.XX  
Energetika: XX.XX  
Hrvatska: XX.XX  
Industrija: XX.XX  
Kreativnost: XX.XX
Znanost: XX.XX



##Plotting most common words in answering career association

```{r echo=FALSE}
##Install neccesary packages
#install.packages('tm')
library(tm)


#' @name Get Mined Text
#' @author Bartol Freškura
#' @description Analysis of the survey free answer question.
#' @param data Dataframe containing answers in form of free text
#' @return Vector containing words sorted by frequency
getMinedText <- function(data){
      
      ##CONSTANTS
      
      #Croatian stopwords
      croStop <- c("i", "ili", "sex", "kita", "kurac", "penis", "bartol", "je", "da","u","ono","sama","ja",
                   "ti","on","ona","ono","mi","vi","me","se","smo","to","za","moje","ali","svo","do","od",
                   "nam","uz","bi", "što", "kako", "da", "ne", "asocira", "koja", "koji", "koje", "svoju",
                   "svom","volim", "volite","sve","tim","tom","toga","svoju","svojem","svoj","svake","sve",
                   "stalnim","sva","vec","veće","vidi","zadimanje","zbog","znači", "sam","samo", "rgnfa",
                   "radi","radimo","steknu","suojesnog","sva","svojem","svoju","trump","tom","toga","tim",
                   "tako","tvrci","usput","vec","vidi","volim","volite", "piso","nosit","odabor","nase","
             našem","naših","nekoj","nekom","nekome","može","moja","kroz","koliko","jest","kao",
             "jako","dovodi","druge","cyxc","doći","čime","and","baviti","aint","zbog","tijekom",
             "mene","kojeg","biti","htjeti","koji", "ako","tko","što","čiji","ciji","koja","kakav",
             "kakve", "svakakve","svakakav","sebe","svoj","tu","one","netko","svatko", "kamo","
             ondje","kada","zašto","donekle","mnogo","ih","gdje","kuda","zato","stoga","s","
             sa","pa","pak","te","ni","niti","dok","god","nego","no","već","saomo","tek",
             "čim","cim","pošto","posto","jer","budući","neka","kao","iako","premda","makar", "donald",
             "fame","car","ćemu","bolj","gradiš","gradimo","imaš","imati","isto","jedn","jednim","
             izrazita","gubitk","money","našem","onoga","oko","one","onog","opi","power","progr","
             svoje", "bitch","fuck","shit","no","yes","ako","kojem","riječ","onom","itd","npr","npr.",
             "ikakv","drugim","jednog","jednoj","nakon","mislim","svoje","ucini","karijera","karijere",
             "karijeru","karijeri","asocira","što", "nešto", "nesto" ,"puno", "niz")
      
      #Put all answers into one vector
      
      careerVec <- paste(data$association.career, collapse = " ")
      
      review_source <- VectorSource(careerVec)
      
      corpus <- Corpus(review_source)
      
      #Set all lower case
      corpus <- tm_map(corpus, content_transformer(tolower))
      
      corpus <- tm_map(corpus, removePunctuation)
      corpus <- tm_map(corpus, stripWhitespace)
      corpus <- tm_map(corpus, removeNumbers)
      #corpus <- tm_map(corpus, stemDocument)###Plotting INA Association
      
      #Remove croatian word with no specific meaning
      corpus <- tm_map(corpus, removeWords, croStop)
      
      dtm <- DocumentTermMatrix(corpus)
      dtm2 <- as.matrix(dtm)
      
      frequency <- colSums(dtm2)
      frequency <- sort(frequency, decreasing=TRUE)
      frequency
      
}
```


```{r}
#install.packages('wordcloud')
library(wordcloud)

frequency <- getMinedText(data)

words <- names(frequency)
wordcloud(words[1:100],max.words = 30,  scale=c(5,0.5), frequency[1:100], random.color = TRUE,colors=brewer.pal(8, "Dark2"))

```

###Most common words Analysis
Ne znam šta da ti ovdje napisem, imaš sliku, naseri koliko možes :D



##Detailed analysis

###Male Female ratio in fields of work
```{r fig.width = 10, fig.height = 7}

plot <- ggplot(data = data, aes(x=(work.field), fill=sex)) + coord_cartesian(ylim=c(0,nrow(data)*0.45))
plot <- plot + geom_bar(width=0.5) + xlab("Field of work") + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=13), axis.title=element_text(size=13))
plot <- plot + scale_fill_discrete(name="Field of work", breaks=c("F","M"), 
                                   labels=c("Female", "Male"))
plot <- plot + scale_x_discrete(labels=c("Finances","IT Support","Logistics","Rafinery and\nMarketing","Research and\nproduction of \n Oil and Gas")) + xlab(NULL)

plot <- plot + ggtitle("Field of Work shown along with male to female rations")
plot


#Percentages
prop.table(table(data$sex, data$work.field))*100
```


###Male Female ratio in Employee satisfaction
```{r fig.width = 10, fig.height = 7}

plot <- ggplot(data = data, aes(x=as.factor(employee.satisfaction), fill=sex)) + coord_cartesian(ylim=c(0,nrow(data)))
plot <- plot + geom_bar(width=0.5) + ylab("Count")
plot <- plot + theme(axis.text=element_text(size=13), axis.title=element_text(size=13))
plot <- plot + scale_fill_discrete(name="",  breaks=c("F","M"), 
                                   labels=c("Female", "Male"))
plot <- plot + scale_x_discrete(labels=c("Yes", "No")) + xlab(NULL)

plot <- plot + ggtitle("Field of Work shown along with male to female rations")
plot


#Percentages
prop.table(table(data$sex, data$employee.satisfaction))*100
```